The markings of the trade: exploring the patterns of olive oil production in Roman Baetica

### 2018-05-30 Paper/jaccardbaetica.tex
lines of conclusion

@@

Probably our results could be interpreted due to several reason according to previous hypotheses.

On the one hand, the use of these amphoric stamps could have been exclusively running by the owner of the workshop to distinguish the amphora workshop (CITAR). The kind of distinction does not seem to be used to specify the quality or value of the product \citep{callender}. 
On the other hand, it can be interpreted somehow a batch systematic organization (CITAR). Considering that Dressel 20 was not marked in several cases (CITAR), some authors point out that potters marked amphorae to prepare and distribute the commodity to be shipped. This method would be used as an identifier to count the number of amphorae of a branch (CITAR). This it could be explain wherefore we found different stamps in a same workshop.

In any case, no podemos precisar a qué se tratase

>>>>

\title{The markings of the trade: exploring the patterns of olive oil production in Roman Baetica}

@@

The results of the case study could be interpreted due to several reason according to previous hypotheses. On the one hand, the use of these amphoric stamps could have been exclusively running by the owner or owners of the workshop to distinguish the amphora workshop (CITAR). This hypotheses would explain the fact that we do not find similar stamps in different workshops, however, we found different amphora stamps in a same workshops that they would be barely difficult to assign different owners. Neither a kind of quality distinction does seem to be used to specify the quality or value of the product \citep{callender}. On the other hand, it can be interpreted somehow a batch systematic organization (CITAR). Considering that Dressel 20 was not marked in several cases, some authors point out that potters marked amphorae to prepare and distribute the commodity to be shipped (CITAR JUAN MOROS). This method would be used as an identifier to count the number of amphorae of a branch (CITAR). This it could be explain wherefore we found different stamps in a same workshop. 
In any case, we do not have enough archaeological evidence that can validated the interpretations presented here and our results are certainly valid only with the context of our case study.
